A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility.

### 2020-08-25 new-paper.Rmd
update 50 acres

Do not deposit data in local file storage that does not provide DOI or accession numbers. For example, [@50Hectares] is hosted on a university server and accessed via FTP. It is not possible to effectively provide effective provenance and credit.

>>>>

Do not deposit data in local file storage that does not provide DOI or accession numbers. For example, [@50Hectares] was hosted on a university server and accessed via FTP for over a decade. It was not possible to effectively provide effective provenance and credit. Only recently was the data deposited in Dryad [@condit-2019].
